Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-09-16 Latex_files/Thesis/chapters/chapter 3/main.tex
updates

Moving a silica bead along an circular path can generate significant fluid 
flow around a larger volume compared to comparable micro-rotors. Using \eqref{eq:galvo_shear} we estimated the shear rate that the surrounding fluid 
would experience at varying speeds. The maximum speed of $7000\ \mu m s^{-1}$
equates to moving the silica bead around a circular path with a frequency of 
$100\ Hz$.
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{galvano_shear_rate.png}
	\caption{Shear rate generated by a silica microsphere ($a = 1.57\ \mu m$) 
		in bulk fluid moving at different speeds. The shear rate is calculated 
		using \eqref{eq:galvo_shear}, with the assumption that the bead is moving
		in a circular path and so the speed is constant through out its path.}
	\label{fig:galvano_shear}
\end{figure}

From figure~\ref{fig:galvano_shear} it is clear that not only is a galvano 
mirror a better option for generating high shear rates but also over a larger 
volume.

@@

\section{Influence of a moving beam front on seed crystals}
\textcolor{red}{Need to write up these results. To summarise the crystal 
	dissolved around the laser focus instead of growing as the seed crystals 
	are in the solution and not close to the air-solution interface}

@@

Secondly, there is the question of how these droplets supply material to the 
bulk crystal. In some instances it is clear that the droplets are being drawn 
into the trap, however, in other instances while there are no droplets close to
the vicinity of the optical trap the crystal continues to grow. If these droplets
are a necessary precursor to induce crystal nucleation then understanding how
they are added to the bulk crystal may help with our understanding of the kinetics
of multi-step nucleation.

>>>>

Moving a silica bead along an circular path can generate significant fluid 
flow around a larger volume compared to comparable micro-rotors. Using \eqref{eq:galvo_shear} we estimated the shear rate that the surrounding fluid 
would experience at varying speeds. The maximum speed of $7000\ \mu m s^{-1}$
equates to moving the silica bead around a circular path with a frequency of 
$100\ Hz$.
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{galvano_shear_rate.png}
	\caption{Shear rate generated by a silica microsphere ($a = 1.57\ \mu m$) 
		in bulk water moving at different speeds. The shear rate is calculated 
		using \eqref{eq:galvo_shear}, with the assumption that the bead is moving
		in a circular path and so the speed is constant through out its path.}
	\label{fig:galvano_shear}
\end{figure}

From figure~\ref{fig:galvano_shear} it is clear that not only is a galvano 
mirror a better option for generating high shear rates but also over a larger 
volume. The only limitation to this method is the effective drag experienced 
by the trapped particle.

@@

\subsection{Influence of a moving beam front on seed crystals}
\textcolor{red}{Need to write up these results. To summarise the crystal 
	dissolved around the laser focus instead of growing as the seed crystals 
	are in the solution and not close to the air-solution interface}

@@

Secondly, there is the question of how these droplets supply material to the 
bulk crystal. In some instances it is clear that the droplets are being drawn 
into the trap, however, in other instances while there are no droplets close to
the vicinity of the optical trap the crystal continues to grow. If these droplets
are a necessary precursor to induce crystal nucleation then understanding how
they provide materials to the bulk crystal may help with our understanding of 
the kinetics of multi-step nucleation.
